Publilia_2019_CHAPTER-4-ants

### 2023-08-25 scripts/old/Publilia_2019_CHAPTER-4-ants.Rmd
minor edits to ensure scripts 01-03 run after overhaul of strats_data

(ants_before_after_p5 <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, !females_removed, last_des_rel2h>4) %>%
  group_by(location) %>%
  filter((Date<=(est_hatch+4))&(Date>=(est_hatch-4))) %>%
  mutate(last_des_date = est_hatch+last_des_rel2h,
         before_after=cut(as.numeric(Date-last_des_date), 
                          breaks=c(-5,-3,-1,0,2,4), labels=c("-4","-2","0","2","4"))) %>%
  ungroup() %>%
  count(before_after, ants_L>0) %>%
  ggplot(data=., aes(x=before_after, y=n, fill=ifelse(`ants_L > 0`,"unattended","attended"))) +
  geom_col(position="fill") +
  ggtitle("Ants before and after hatching (last desert nymphs)") +
  ylab("Proportion of clutches") +
  xlab("Days since hatch"))
```
FUUUUUUUUCKKKKK!!!!!!!!!!!!
Removing a mother results in a decrease in the probability of the clutch being attended by ants in the four days following removal ().
```{r}
ants_before_after_p1.data <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, females_removed) %>%
  mutate(last_des_date = est_hatch+last_des_rel2h) %>%
  filter((Date<=(last_des_date+4))&(Date>=(last_des_date-2))) %>%
  filter(Date!=(last_des_date-3), Date!=(last_des_date-1)) %>% #fix higher sampling rate before removal
  group_by(location) %>%
  filter(any(Date==(last_des_date-2))) %>% # remove any clutches where there are missing data before des
  mutate(before_after=cut(as.numeric(Date-last_des_date), 
                          breaks=c(-3,0,4), labels=c("4 days before removal", "4 days after removal"))) %>%
  ungroup() %>%
  select(location,Date, last_des_date, before_after, ants_L)

>>>>

(ants_before_after_p5 <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, !females_removed, last_des_rel2h>4) %>%
  group_by(location) %>%
  filter((Date<=(est_hatch+4))&(Date>=(est_hatch-4))) %>%
  mutate(last_des_date = est_hatch+last_des_rel2h,
         before_after=cut(as.numeric(Date-last_des_date), 
                          breaks=c(-5,-3,-1,0,2,4), labels=c("-4","-2","0","2","4"))) %>%
  ungroup() %>%
  count(before_after, ants_L>0) %>%
  ggplot(data=., aes(x=before_after, y=n, fill=ifelse(`ants_L > 0`,"unattended","attended"))) +
  geom_col(position="fill") +
  ggtitle("Ants before and after hatching (last desert nymphs)") +
  ylab("Proportion of clutches") +
  xlab("Days since hatch"))
```

Removing a mother results in a decrease in the probability of the clutch being attended by ants in the four days following removal ().
```{r}
ants_before_after_p1.data <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, females_removed) %>%
  mutate(last_des_date = est_hatch+last_des_rel2h) %>%
  filter((Date<=(last_des_date+4))&(Date>=(last_des_date-2))) %>%
  filter(Date!=(last_des_date-3), Date!=(last_des_date-1)) %>% #fix higher sampling rate before removal
  group_by(location) %>%
  filter(any(Date==(last_des_date-2))) %>% # remove any clutches where there are missing data before des
  mutate(before_after=cut(as.numeric(Date-last_des_date), 
                          breaks=c(-3,0,4), labels=c("4 days before removal", "4 days after removal"))) %>%
  ungroup() %>%
  select(location,Date, last_des_date, before_after, ants_L)
